D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-01 ootavacuous.tex
March 1 Alan Stern feedback
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Third case: $W'$ lies in the divergent portion of $H$.
This happens when $W'$ comes after the conditional or computed branch
which marks the end of the common period by going different ways in
$H$ and $G$.
Just as in the previous case, since the branch behaves differently in
the two executions it must be ordered after one of the $R'_i$ loads.
And then so must $W'$, because the execution of any instruction following
a conditional- or computed-branch instruction is ordered after that
branch.
QED.

>>>>

Third case: $W'$ lies in the divergent portion of $H$.
This happens when $W'$ comes after the conditional or computed branch
which marks the end of the common period by going different ways in
$H$ and $G$.
Just as in the previous case, since the branch behaves differently in
the two executions it must be ordered after one of the $R'_i$ loads.
And then so must $W'$, because any instruction following a conditional-
or computed-branch instruction must commit after that branch
commits.\footnote{
	But note that a load might obtain its value from memory before
	previous instructions have committed.}
QED.
